To Airbnb?: A Question of Revenue

### 2018-07-18 review/response_to_reviewers.Rmd

---
title: "Reviewer Responses: To Airbnb?: A Question of Revenue"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "July 22nd, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

## Reviewer #1

Thank you for your helpful and encouraging comments.

* Thank you for pointing out the three typographical errors on pages 10, 30 and 31.  We have corrected these.

* We agree that there are many future avenue of research that can be pursued here, especially as data quality and quantity in this direction improves.  We appreciate your understanding of the difficulty of working with limited data and the necessity of our assumptions.

* Regarding the structure of cities and the generalizability of the findings.  We agree that Melbourne, as a world class tourist destination and (arguably) the world's most livable city, does provide an example that does not necessarily translate well to a second or third tier city in many other parts of the world. As you noted, this desire for both tourists and residents to occupy the same space is what, in our minds, made this the ideal city for this analysis. We do feel that many of the world's first class cities are experiencing the same phenomenon -- namely that a large segment of the local population desires the same walkable, vibrant locations that tourists do, thus leading to increased demand and increasingly contentious discussions over the negative externalities of a thriving short-term rental market.  We've added some language in the beginning of the 'Limitations' section that addresses the issues of generalizability.  Finally, we are in the process of additional data collection to expand the research to a more representative sample.

## Reviewer #2

5. Thank you for pointing out this typographic error.  We have corrected it.

### 2018-07-18 papers/full_paper.Rmd
Reviews:  Review 1 responses

There are a number of limitations to this research.  There are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.  Part of the difficulty in estimating potential short-term rates for long-term properties is that the short-term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.  Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short-term market.  It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com.

>>>>

There are a number of limitations to this research.  First and foremost may be the generalizability of this work.  Melbourne is one of the primary examples of a world-class city in which local residents and tourists often (and fiercely) compete for the same urban spaces.  As such, the results we find here are likely to be much more applicable and generalizable to large, thriving cities with attractive urban neighborhoods such as London, San Francisco and Hong Kong, rather than secondary or tertiary metropolitan areas.  From investment and policy perspectives, however, it is in these larger centers that the findings of this research are most useful in a practical sense.

Next, there are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.  Part of the difficulty in estimating potential short-term rates for long-term properties is that the short-term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.  Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short-term market.  It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com.
